Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-07-26 GNproof.tex
minor edits to GNproof

\begin{proof}
We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.  Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$. If $V(p_r) \subseteq [I_i(p_r)-1,j_m]$, then since $q$ is inside $p_r$ we also have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex]. In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case. If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s)$; further, we can assume that $q$ is not supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$. This yields one of the configurations in Figure~\ref{fig:awkward induction step}.

\begin{figure}[h]
\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$. Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
\end{figure}

Now repeat the argument above with $p_s$ in place of $p_r$; this is valid since we only really need to know that $q$ is inside $p_s$ with respect to $<_{a_s - 1}$. Then either $V(p_s) \subseteq [I_i(p_s)-1,j_m]$, in which case we are done (as above), or there exists some $p_t \in Q_{l-3}$ and we continue to iterate the argument. Since there are finitely many propagators and we are guaranteed that $V(p_*) \subseteq [I_i(p_*)-1,j_m]$ if we ever reach $p_* \in Q_0$, we eventually construct a propagator that constrains $q$ and ensures that $q \in \cP_{m-1}$. This completes the induction step.

>>>>

\begin{proof}
We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$. Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show: 
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately: the algorithm is  so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption. If the other end of $p_r$ (i.e. the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$ then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex]. In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.

If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$. Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$. Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.

\begin{figure}[h]
\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
\caption{This picture isn't quite the one we need any more, but it should help to illustrate the claim about $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
\end{figure}

Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_r)$. Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step.
